Multisensor Architecture for an Intersection Management System

### 2018-11-13 ch2-mdf_ims.tex
updated figures as required
Final draft
Corrections in ch 1, 2 and 5
Added TODOs

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.4]{fig/2/jdlmodel.png}
\caption{JDL fusion model. (from \cite{Hall1997}).}
\label{JDLmodel}
\end{figure}

\todo{Create custom figure}

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.4]{fig/2/fusionClasses.png}
\caption{Five classes of Multisensor Fusion.}
\label{fusionClasses}
\end{figure}

\todo{Increase font size of this figure}

@@

Elmenreich in \cite{Elmenreich2007} classify fusion models in three categories: Abstract models, generic architectures and rigid architectures. Abstract model are not intended to show how to implement a sensor fusion system, but to explain which processes are done in it. Generic architectures gives an outline on how a system could be implemented in an application, but do not specify what type of hardware, database or communication system could be used. Finally, rigid architectures, are a good guide for implementation  of data fusion in certain applications, at the cost that several design decisions have been already taken, making expensive the migration to another architecture.

@@

Intersection monitoring is a required task to be done within intelligent transportation systems for high-level applications like traffic analysis, counting and classification of vehicles or pedestrians, event prediction, incident detection and security and surveillance systems. Those applications have to take into account some of the elements depicted in figure \ref{arch} and developments in IMS have a wide range of approaches and objectives. In order to study IMS applications, five components have been defined, which are present on these applications, and on most cases, more than one component could be involved in the same development. In figure  \ref{imsComps} a graph is presented, showing aforementioned components and elements within them, and next, a description of each component is given.

>>>>

\epigraph{"The goal is to turn data into information, and information into insight"}{Carly Fiorina}
%\epigraph{"Not everything that can be counted counts, and not everything that counts can be counted"}{Albert Einstein}

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.7]{fig/2/jdlmodel.pdf}
\caption{JDL fusion model. (from \cite{Hall1997}).}
\label{JDLmodel}
\end{figure}

\todo{Describe level 4 and highlight levels}

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/2/mfi.pdf}
\caption{Five classes of Multisensor Fusion.}
\label{fusionClasses}
\end{figure}

%\todo{Increase font size of this figure}

@@

\todo{Highlight architectures types}
Elmenreich in \cite{Elmenreich2007} classify fusion models in three categories: Abstract models, generic architectures and rigid architectures. Abstract model are not intended to show how to implement a sensor fusion system, but to explain which processes are done in it. Generic architectures gives an outline on how a system could be implemented in an application, but do not specify what type of hardware, database or communication system could be used. Finally, rigid architectures, are a good guide for implementation  of data fusion in certain applications, at the cost that several design decisions have been already taken, making expensive the migration to another architecture.

@@

Intersection monitoring is a required task to be done within intelligent transportation systems for high-level applications like traffic analysis, counting and classification of vehicles or pedestrians, event prediction, incident detection and security and surveillance systems. Those applications have to take into account some of the elements depicted in figure \ref{arch} and developments in IMS have a wide range of approaches and objectives. In order to study IMS applications, five components have been defined, which are present on these applications, and on most cases, more than one component could be involved in the same development. In figure  \ref{imsComps} a graph is presented, showing aforementioned components and elements within them, and next, a description of each component is given.
\todo{Fix V2I label}

### 2018-11-13 ch3-arch_sys.tex
Added TODOs

@@

%\todo{Simulators description (?)}

@@

Redis is also used as in-memory storage for configuration data that is not part of the processing flow, like sensor parameters, intersection model and control options. This information is loaded into Redis from a JSON file and it is available for any client requiring it.

@@

The sensors sets are composed of zero or more sensor objects, as defined previously. An Area class is defined as having a bounding box and a label	. From this class, a derived class, Leg, is defined for containing additional information about the legs of the intersection, such as heading of the leg, approaching or departure type. In figure \ref{data_model} is shown an UML diagram for the aforementioned classes and their relationships

@@

Data exchanged between processing blocks or any paramater stored in Redis, is formatted using JavaScript Object Notation (JSON), allowing to use any JSON parser/formatter available in many languages, even it is possible to create simple scripts to interact with the system.

@@

\subsubsection{Tools and Utilities}
\begin{description}

>>>>

\todo{Check stages description and figure}

@@

\todo{Simulators description (?)}

@@

Redis is also used as in-memory storage for configuration data that is not part of the processing flow, like sensor parameters, intersection model and control options. This information is loaded into Redis from a JSON file and it is available for any client requiring it.
\todo{Define JSON HERE!!!!}

@@

The sensors sets are composed of zero or more sensor objects, as defined previously. An Area class is defined as having a bounding box and a label. From this class, a derived class, Leg, is defined for containing additional information about the legs of the intersection, such as heading of the leg, approaching or departure type. In figure \ref{data_model} is shown an UML diagram for the aforementioned classes and their relationships

@@

\todo{Move JSON definition from here!!!}
Data exchanged between processing blocks or any paramater stored in Redis, is formatted using JavaScript Object Notation (JSON), allowing to use any JSON parser/formatter available in many languages, even it is possible to create simple scripts to interact with the system.

@@

\end{description}
\todo{Check formatting here}
\subsubsection{Tools and Utilities}
\begin{description}
